---
title: "Auswertung"
format: html
editor: visual
---

## Environment info

Distro: Linux Fedora 43 for Workstation\
Kernel: Linux 7.0.12-101.fc43.x86_64\
R: 4.5.3

CPU: Intel 12th Gen. Core i5-12600K (x86_64) / 16 logical cores / 4.90 GHz boost clock\

## Environment variables

```{r setup, include=FALSE, echo=FALSE}
require("knitr")
opts_knit$set(root.dir = "/home/simon/Documents/Masterprojekt 2026/Datensätze/")

```

Compile `gesis-appkit` module from source:

```{r}
install.packages("remotes")

#compile from source
remotes::install_gitlab("gesis-appkit/appkitr")
```

```{r}
#| echo: false

#import modules
library(appkitr)
library(dplyr)
library(tidyr)
library(labelled)
library(psych)
library(ggplot2)
```

## Data pre-processing

Read files:

```{r}
#| echo: false
#read data
socio_raw <- read_appkit_survey("Soziodemographie/17_Juni_2026/")
vormittag_raw <- read_appkit_survey("Vormittag/17_Juni_2026/")
nachmittag_raw <- read_appkit_survey("Nachmittag/17_Juni_2026/")
abend_raw <- read_appkit_survey("Abend/17_Juni_2026/")
```

Cleaning empty cases:\
*(= surveys which have never been completed by the participant)*

```{r}
#drop na rows
socio <- socio_raw %>% 
  drop_na("committed")

vormittag <- vormittag_raw %>% 
  drop_na("committed")

nachmittag <- nachmittag_raw %>% 
  drop_na("committed")

abend <- abend_raw %>% 
  drop_na("committed")
```

Cleaning cases with less than 20% completion rate:

```{r}
vormittag <- vormittag %>% 
  group_by("personalParticipantCode") %>% 
  filter(n() > 4) %>% 
  ungroup()

nachmittag <- nachmittag %>% 
  group_by("personalParticipantCode") %>% 
  filter(n() > 4) %>% 
  ungroup()

abend <- abend %>% 
  group_by("personalParticipantCode") %>% 
  filter(n() > 4) %>% 
  ungroup()
```

Removing unnecessary columns:

```{r}
#| echo: false
#drop unnecessary columns
socio_reduced <- socio_raw %>% 
  select("personalParticipantCode", 
         "s1_alter", 
         "s2_geschlecht", 
         "s3_bildung", 
         "f1_frequenz_tiktok",
         "f1_frequenz_instagram",
         "f1_frequenz_youtube")

vormittag_reduced <- vormittag %>% 
  select("personalParticipantCode",
         "f2_filter_nutzung",
         "f3_nutzung_plattform",
         "f4_valenz",
         "f5_arousal",
         starts_with("f6_habitualisiert"),
         starts_with("f7_beduerfnis"))

nachmittag_reduced <- nachmittag %>% 
  select("personalParticipantCode",
         "f2_filter_nutzung",
         "f3_nutzung_plattform",
         "f4_valenz",
         "f5_arousal",
         starts_with("f6_habitualisiert"),
         starts_with("f7_beduerfnis"))

abend_reduced <- abend %>% 
  select("personalParticipantCode",
         "f2_filter_nutzung",
         "f3_nutzung_plattform",
         "f4_valenz",
         "f5_arousal",
         starts_with("f6_habitualisiert"),
         starts_with("f7_beduerfnis"))

```

Extract labels for later.\
We do not really need labels but the data comes with them so we might as well keep them.

```{r}
#we only need labels for one because they are all identical
labels_esm <- var_label(vormittag_reduced)

#we do not need labels for socio because left_join keeps them
```

Merging datasets:

```{r}
#add identifier for day of time
vormittag_reduced <- vormittag_reduced %>% 
  mutate(time_of_day = 1)

nachmittag_reduced <- nachmittag_reduced %>% 
  mutate(time_of_day = 2)

abend_reduced <- abend_reduced %>% 
  mutate(time_of_day = 3)

#merge vormittag, nachmittag & abend
merged_dataset <-bind_rows(vormittag_reduced, nachmittag_reduced, abend_reduced)

#add socio
merged_dataset <- merged_dataset %>% 
  left_join(socio_reduced, by = "personalParticipantCode")

#add labels
var_label(merged_dataset) <- labels_esm 
```

## Auswertung

### Sozio

```{r}
psych::describe(socio_reduced)
```

```{r}
#density distribution for age
ggplot(socio_reduced, aes(x = s1_alter)) +
  geom_density(fill = "lightblue", alpha = 0.5) +
  theme_minimal()

```
